Do return series have power-law tails with the same index?

### 2017-05-05 papers/FX/draft.tex
Fixed the bibliography.

generalization GO-GARCH by van der Weide \cite{van2002go},  the Full Factor GARCH model of Vrontos et al.

@@

model of Lanne and Saikkonen  \cite{lanne2007modeling}. These

>>>>

generalization GO-GARCH by van der Weide \cite{Weide2002},  the Full Factor GARCH model of Vrontos et al.

@@

model of Lanne and Saikkonen  \cite{lanne2007modelling}. These
